An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
remove inline
Signed-off-by: andrew <andrew@textile.io>

\begin{example}
\begin{lstlisting}
// KeyBook stores log keys
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}
\caption{A KeyBook storing log keys.}
\end{example} \label{ex:KeyBook}

>>>>

\begin{example}
\begin{lstlisting}
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}
\caption{A KeyBook storing log keys.}
\end{example} \label{ex:KeyBook}
